---
title: "Problem Set 4"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## I. Creating workflows with the Portal Project
For each of the following prompts, please:
a) Identify the information needed
b) Identify the datasets that have this information
c) Write the in-English workflow needed to go from raw data to question
d) Write the R code using tidyverse syntax to go from raw data to question. Note: it's good practice to comment your code with hashtags as you go. You often may want to visualize the data to enter the question.


### 1) What is the average weight of each taxa?
a) Information needed:
b) Datasets needed:
c) English workflow:

d) R workflow:
```{r}

```

### 2) What is the percentage of each species in each taxa?
a) Information needed:
b) Datasets needed:
c) English workflow:

d) R workflow:
```{r}

```


### 3) How many specimens of each sex are there for each year?
a) Information needed:
b) Datasets needed:
c) English workflow:

d) R workflow:
```{r}

```


### 4) What are the minimum, maximum and average weight for each species of Rodent?
a) Information needed:
b) Datasets needed:
c) English workflow:

d) R workflow:
```{r}

```


### 5) What is the average hindfoot length for male and female rodent of each species? Is there a Male / Female difference?
a) Information needed:
b) Datasets needed:
c) English workflow:

d) R workflow:
```{r}

```


### 6) What is the average weight of each rodent species over the course of the years? Is there any noticeable trend for any of the species?
a) Information needed:
b) Datasets needed:
c) English workflow:

d) R workflow:
```{r}

```

