---
title: "Problem Set 3"
output: html_document
---

*Please submit as an html file and show all your work (i.e., do NOT put echo = FALSE in your chunk)*

## 1) TOTAL BIOMASS WITH OVER TIME 
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001

#### i) What did Haddad et al. 2002 find? See text and Figure 6  
- What happened to total biomass during the drought?  
- What years, treatments and fields did they include in Figure 6a?

### WORKFLOW A: Mimic Figure 6a. Please make a graph of mean total biomass in the successional field control plots over time. Include standard errors around each plotted point. 

Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?ple001

#### ii) Write out the workflow you will use in English.
- What QAQC will you do beforehand? What data will you include and what will you drop?  
- How will you manipulate the data to create the graph?  


#### iii) Write out and run the workflow in tidyverse R.
Please comment your code. Here's the data import to get you going (uncomment the data import - make sure this .Rmd and the .csv files are stored in the same folder!):
```{r, message = F}
library(tidyverse)
#cdrplant <- read_csv("e001_Plant aboveground biomass data.csv", skip = 726)
```


## 2) C:N RATIOS WITH N-DEPOSITION
Check out  http://www.cedarcreek.umn.edu/research/experiments/e001  

#### i) What did Wedin and Tilman 1996 find? See text and Figure 7  

### WORKFLOW: Please make a graph of the ratio of C:N in aboveground biomass in response to the amount of nitrogen added by species. Include standard error bars around each plotted point.
Unlike Wedin, these data are just from Field C, so no need to represent each field separately.  
The sample sizes for some species and N levels are very low, please only include species that have at least 4 replicates in each of at least 3 nitrogen levels.  NOTE: It is okay to iteratively check this (e.g., plotting first and then identifying which species match these criteria)
Metadata here: http://www.cedarcreek.umn.edu/research/data/dataset?nbe001

#### ii) Write out the workflow you will use in English.
- What QAQC will you do beforehand?  
- How will you manipulate the data to create the graph?  


#### iii) Write out and run the workflow in tidyverse R.  
Please comment your code. Here's the data import to get you going (uncomment the data import):
```{r}
#cdrCN <- read_csv("e001_Plant aboveground biomass carbon and nitrogen.csv", skip = 491) 
```

*QUESTION: How does aboveground tissue C:N ratios change with N enrichment? Do patterns appear consistent across species?*
