---
title: "Problem Set 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# TIDY DATA

## Read in the data 

```{r, message = F, warning=F}
# Load the tidyverse
library(tidyverse)

# Read in the data
rawdat <- read_csv("Niwot_Salix_2014_WillowSeedlingSurvey.csv", skip = 10)

```

### 1) Learn about the data:
- QUESTION: Where are the meta data for this file?  

- QUESTION: What is this format of data useful for?  

- QUESTION: What is this format of data not useful for?   


### 2) Fill in missing variables:
Using the example below, fill in the rest of the relevant columns of filldat
```{r}
## From the book: Sometimes when a data source has primarily been used for data entry, 
## missing values indicate that the previous value should be carried forward:
## Compare filldat and rawdat
filldat <- rawdat %>%
  fill(block) %>%
  print

```

### 3) Common problem 1: Column headers are values, not variable names

- QUESTION: Does this problem exist in this dataset? If so, how would you change it?

- TASK: In the chunk below, create a new tibble called cleandat that starts with filldat and then solves this tidy data problem

- TASK: Go ahead and remove the "w_" from values in your new column


```{r}

```


### 4) Common problem 2: Variables are stored in both rows and columns

- QUESTION: Does this problem exist in this dataset? If so, how would you change it?


- TASK: If necessary, copy your cleandat workflow below and add code that addresses this problem

```{r}

```



### 5) Common problem 3: Multiple variables are stored in one column 

- QUESTION: Does this problem exist in this dataset? If so, how would you change it? Note: there might be multiple examples of this. Check the meta data on numeric versus alphabetical numbering.

- TASK: If necessary, copy your cleandat workflow into the chunk below and add code that addresses this problem

```{r}

```


### 6) Common problem 4: Multiple types of observational units are stored in the same table

- QUESTION: Does this problem exist in this dataset? If so, how would you change it?  


- TASK: If necessary, copy your cleandat workflow below and add code that addresses this problem. Note: You may need to make new tibbles.

```{r}

```

### 7) Common problem 5: A single observational unit is stored in multiple tables

- QUESTION: Does this problem exist in this dataset? If so, how would you change it?


- TASK: If necessary, copy your workflow below and add code that addresses this problem

```{r}

```

### 8) Put it together graphically

- QUESTION: How does snow addition, temperature and nitrogen affect willow seedling survival and growth?

- VISUALIZE IT:  

```{r}

```

- INTERPRET IT:


