---
title: "Exploratory Data Visualization"
output:
  pdf_document: default
  html_document: default
---

## In-class exercise: 
In groups of four, plot the data in Table 1 to answer the following questions:

1) Do mortality rates change with air pollution concentration? 
2) Does accounting for season change how you perceive the relationship between mortality and pollution? 

Please make your plot large enough to present to the class.

```{r, echo=F}
## Create simulated data for air pollution and mortality
wDM <- sort(sample(c(200:250), size = 8, replace = TRUE))
wPM <- sort(sample(c(1:20), size = 8, replace=T))

fDM <- sort(sample(c(180:230), size = 8, replace = TRUE))
fPM <- sort(sample(c(5:30), size = 8, replace=T))

spDM <- sort(sample(c(165:220), size = 8, replace = TRUE))
spPM <- sort(sample(c(8:35), size = 8, replace=T))

sumDM <- sort(sample(c(150:200), size = 8, replace = TRUE))
sumPM <- sort(sample(c(10:40), size = 8, replace=T))

## Put it together
togDM <- c(wDM, sumDM, fDM, spDM)
togPM <- c(wPM, sumPM, fPM, spPM)

a <- togPM
b <- togDM
season <- c(rep("winter", 8), rep("summer", 8), rep("fall", 8), rep("spring", 8))

alltog <- data.frame(season, a,b)
names(alltog)[2:3] = c( "PM10", "Mortality")

#write.csv(alltog, "PollutionData_Exercise.csv")
```

```{r setup, include=T, echo=F}
library(knitr)
mydat <- read.csv("PollutionData_Exercise.csv")
names(mydat)=c("Season", "PM10 Concentration", "Daily mortality (all causes)")
kable(mydat)
```


Table 1. Simulated data of eight years of seasonal air quality, measured as particulate matter (PM10) and centered around the mean, and daily mortality rates in the United States.